---
title: "Machine Learning Project"
author: "Samuel Pinkava"
date: "August 23, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE)
```

##Creating the cross-validation set

First, I clean the data by getting rid of any columns with missing data.

Second, I will combine any columns that are highly correlated.

Then, I will split the training set into a training set and a testing set. 
I will save the given testing set as a validation set at the end.

```{r}
library(caret)
set.seed(82318)
training_URL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
pmlData <- read.csv(training_URL,na.strings=c("NA",""))
cleanPmlData <- pmlData[,complete.cases(t(pmlData))]
inTrain = createDataPartition(cleanPmlData$classe, p = 0.3)[[1]]
training = cleanPmlData[inTrain, ]
testing = cleanPmlData[-inTrain, ]
```

##Creating the model
To create the model, I will first use PCA to combine any columns that are
highly correlated.

Then, I am going to use the random forest, linear discriminant 
analysis, and a combined model. I will then select whichever one is best.

```{r}
mod_rf <- train(classe ~ ., data = training, method = "rf", 
                trControl=trainControl(method="cv",number=3))
mod_lda <- train(classe ~ ., data = training, method = "lda")
pred_rf <- predict(mod_rf, testing)
pred_lda <- predict(mod_lda, testing)
predDF <- data.frame(pred_rf, pred_lda, classe = testing$classe)
combModFit <- train(classe ~ ., method = "rf", data = predDF)
combPred <-  combPred <- predict(combModFit,predDF)
```

Next I find the accuracy of each model.

```{r}
confusionMatrix(pred_rf,testing$classe)$overall
confusionMatrix(pred_lda,testing$classe)$overall
confusionMatrix(combPred,testing$classe)$overall
```

As we can see, the linear discriminant analysis is the same as the combined model.
We will therefore use LDA, as it is the simplest model.

There is no need to do a cross validation, as the lda model was entirely decided 
using the training set.

